\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-25 paper/main.tex
Profread and made minor changes

\sloppy Several application domains (e.g., transportation and
medicine) use AI as part of their solutions. Deep Learning~(DL)
libraries, such as \jax, \torch{}, and \tf{}, provide the building
blocks for the AI components of these applications.  Unfortunately, as
any piece of software, these libraries contain bugs. An impressive
number of techniques have been recently proposed to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe these techniques propose an independent evaluation
methodology. These techniques do \emph{not} use a reference database
of reproducible bugs to evaluate their effectiveness. The lack of an
evaluation standards is a serious obstacle to a fair and rigorous
comparison of techniques and hinders research progress.

@@

\begin{enumerate}[leftmargin=0.2in]
\item developers should be able to write tests scripts in Python;
\item ~they should be able to handle nighly builds and specific
  versions of CUDA (\textsection~\ref{sec:challenges});
\item they should be able to integrate fuzzing tools in the framework.
\end{enumerate}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (conda enviroment or docker). Co-incidentally,
all bugs that require a GPU are reproduced using docker
containers, i.e. the column conda-docker matches what would have been
observed with a column CPU-GPU, to indicate if the bug can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.

@@

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label (bug), the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard cases that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we do a deeper analysis on these bugs. We find some cases that
are related to building/installation/problematic unit tests instead of
bugs in the core API functionality, as well as some bugs that lack any
code snippet provided with the bug report to reproduce the bug. These
bugs can be detected and discarded at this stage.
We assess the reproducibility of a bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
or can not be reproduced due to an expired nightly build that can no
longer be accessed. We successfully reproduce the bug if none of these
issues are present by
creating the enviroment detailed in the report, and we include the
corresponding artifacts in our dataset. We use a virtual enviroment
(conda~\cite{venv}) when the bug can be reproduced on a CPU, and we use docker
containers~\cite{merkel2014docker} with appropriate CUDA drivers when the bug 
requires a GPU.
Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

@@

\vspace{0.5ex}\noindent\textbf{Handling bugs in specific GPU-CUDA
  versions requires OS changes:} Some GPU-related bug instances can
only be reproduced with specific versions of CUDA~\cite{cuda},
NVIDIA's platform and API for programming GPUs. These instances
require specific CUDA drivers to be installed on the system. Python
virtual enviroments are not designed to enable change of OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers~\cite{merkel2014docker} for the bug instances
that require changes in drivers.

\subsection{Method}
\label{sec:method}
The following steps show the method we use to create bug instances:
\vspace{-5mm}
\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Identify the version of the library used to report the bug along with other dependencies;
  \item Write a \CodeIn{requirements.txt} file with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}
\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signal and the assertion passes.
% \Fix{Please review and revise}

@@

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool (e.g. \CodeIn{run\_freefuzz\_docker.sh}); (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
execution log with the expected errors (\CodeIn{postprocess.py}) needs to be provided.
% \Fix{name
%   these scripts here and refer back to them in the text below} 
The
directory \CodeIn{tool-integration} contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
% \Fix{remove this paragraph. Explain the steps when they appear. It is difficult
%   to follow}
% \Fix{up to here}
We demonstrate the integration of FreeFuzz~\cite{wei2022free}. The
following script creates a Docker container for FreeFuzz.

@@

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} build the docker
container that encapsulates FreeFuzz.

@@

The following script runs FreeFuzz on all bugs associated with version
2.2.1+cu121 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports how
many bugs that are reproducible with this version of the library were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.

>>>>

\sloppy Several application domains (e.g., transportation and
medicine) use AI as part of their solutions. Deep Learning~(DL)
libraries, such as \jax, \torch{}, and \tf{}, provide the building
blocks for the AI components of these applications.  Unfortunately, as
any piece of software, these libraries contain bugs. An impressive
number of techniques have been recently proposed to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe these techniques propose an independent evaluation
methodology. These techniques do \emph{not} use a reference database
of reproducible bugs to evaluate their effectiveness. The lack of an
evaluation standard is a serious obstacle to a fair and rigorous
comparison of techniques and hinders research progress.

@@

\begin{enumerate}[leftmargin=0.2in]
\item developers should be able to write test scripts in Python;
\item they should be able to handle nighly builds and specific
  versions of CUDA (\textsection~\ref{sec:challenges});
\item they should be able to integrate fuzzing tools in the framework.
\end{enumerate}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (conda enviroment or docker). Co-incidentally,
all bugs that require a GPU are reproduced using docker
containers, i.e. the column conda-docker matches what would have been
observed with a column CPU-GPU, to indicate if the bug can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown of error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on a GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.

@@

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label (bug), the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard cases that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we do a deeper analysis on these bugs. We find some cases that
are related to building/installation/problematic unit tests instead of
bugs in the core API functionality, as well as some cases that are simply API misuses, not bugs. These
bugs can be detected and discarded at this stage.
We assess the reproducibility of a bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
or can not be reproduced due to requiring a debug build that only the developers can access. We successfully reproduce the bug if none of these
issues are present by
creating the enviroment detailed in the report, and we include the
corresponding artifacts in our dataset. We use a virtual enviroment
(conda~\cite{venv}) when the bug can be reproduced on a CPU, and we use docker
containers~\cite{merkel2014docker} with appropriate CUDA drivers when the bug 
requires a GPU.
Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

@@

\vspace{0.5ex}\noindent\textbf{Handling bugs in specific GPU-CUDA
  versions requires OS changes:} Some GPU-related bug instances can
only be reproduced with specific versions of CUDA~\cite{cuda},
NVIDIA's platform and API for programming GPUs. These instances
require specific CUDA drivers to be installed on the system. Python
virtual environments are not designed to enable changing OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers~\cite{merkel2014docker} for the bug instances
that require changes in drivers.

\subsection{Method}
\label{sec:method}
The following steps show the method we use to create bug instances:
\vspace{-5mm}
\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Identify the version of the library used to report the bug along with other dependencies;
  \item Write a \CodeIn{requirements.txt} file with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container~\cite{merkel2014docker}) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} is the
    affected library and \CodeIn{bug-id} is the issue number of the bug report.
    % is a fresh identifier of the
    % bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}
\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signal and the assertion passes.
% \Fix{Please review and revise}

@@

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool (e.g. \CodeIn{run\_freefuzz\_docker.sh}); (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
execution log with the expected errors (\CodeIn{postprocess.py}).
% \Fix{name
%   these scripts here and refer back to them in the text below} 
The
directory \CodeIn{tool-integration} contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
% \Fix{remove this paragraph. Explain the steps when they appear. It is difficult
%   to follow}
% \Fix{up to here}
We demonstrate the integration of FreeFuzz~\cite{wei2022free}. The
following script creates a Docker container for FreeFuzz.

@@

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} builds the docker
container that encapsulates FreeFuzz.

@@

The following script runs FreeFuzz on all bugs associated with version
2.2.1+cu121 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}). The script reports how
many bugs that are reproducible with this version of the library were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.
